\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Add "a"
I think "prior" like that isn't actually wrong, but it rings off. The usual phrase would be "prior to", and that doesn't work here.

\item[-] \textbf{Voting Stage:} All members - including current and prospective council members, \textit{back} candidates for the next term. Backing refers to staking in support of the candidacy of a member in the candidate pool. Each backing is a sealed commitment to particular candidate, where the seal is simply salted hashing of the candidate identifier. A member may reuse tokens already staked behind an existing council member, to a member of the candidate pool, which is called \textit{transferring backing stake}.

@@

As mentioned prior, for example in section \ref{sec:member}, it should be possible to onboard users who do not hold any tokens. This activity, which is called \textit{screening}, allows the platform to accommodate new users who can try the platform within certain constraints. However, the combination of no robust identity system and allowing users to consumer resources without paying on the margin creates its own set of new problems. These resources need not only be in the form of tangibles like compute and storage, but also things like peer member attention. Not only does this result in wasteful overutilisation, but perhaps more importantly, it allows platform participants to shape their own payouts by at a low cost, since resource use is often tied to payouts. For example viewing content will divert larger share of payout to the publisher.

>>>>

\item[-] \textbf{Voting Stage:} All members - including current and prospective council members, \textit{back} candidates for the next term. Backing refers to staking in support of the candidacy of a member in the candidate pool. Each backing is a sealed commitment to a particular candidate, where the seal is simply salted hashing of the candidate identifier. A member may reuse tokens already staked behind an existing council member, to a member of the candidate pool, which is called \textit{transferring backing stake}.

@@

As mentioned before, for example in section \ref{sec:member}, it should be possible to onboard users who do not hold any tokens. This activity, which is called \textit{screening}, allows the platform to accommodate new users who can try the platform within certain constraints. However, the combination of no robust identity system and allowing users to consumer resources without paying on the margin creates its own set of new problems. These resources need not only be in the form of tangibles like compute and storage, but also things like peer member attention. Not only does this result in wasteful overutilisation, but perhaps more importantly, it allows platform participants to shape their own payouts by at a low cost, since resource use is often tied to payouts. For example viewing content will divert larger share of payout to the publisher.
